The Challenges of Teaching Technical Writing

### 2019-03-13 Choosing_classifier.Rmd
update

---
title: "Choosing a Text Classifier Method"
date: "2/21/2019"
bibliography: library.bib
biblio-style: apalike
---

@@

#Choosing a Text Classifier Method
The many methods for classifying texts fall into three general categories:

*  Pattern matching strategies (does a particular phrase appear?)
*  Algorithms (how closely does the query text meet pre-set criteria?)
*  Neural networks (the network decides its own criteria, aka machine learning)

This edited excerpt nicely describes the overall approach and problems of text classification. It is from: **xxxxx**

@@

This classifier is “naive” because each word is treated as having no connection with other words in the sentence being classified. In other words it assumes independence between "features," in this case, words.

For example, in the sentence “the fox jumped over the log”, there is no relationship between “jumped” and “fox” or “log”. In NLP, this collection of words is referred to as “a bag of words”. While this is incredibly naive, the classifier isn’t attempting to understand the meaning of a sentence, it’s trying to classify it.

Pattern Matchers
Early chatbots used **pattern matching** to classify text and produce a response. This is often referred to as “brute force” as the author of the system needs to describe every pattern for which there is a response.

A standard structure for these patterns is “AIML” (artificial intelligence markup language). Its use of the term “artificial intelligence” is quite an embellishment, but that’s another story.

@@

It knows who a physicist is only because his or her name has an associated pattern. Likewise it responds to anything solely because of an authored pattern. Given hundreds or thousands of patterns you might see a chatbot “persona” emerge.

In 2000 a chatbot built by John Denning and colleagues using this approach was in the news for passing the "Turing test." It emulated the replies of a 13 year old boy from Ukraine (broken English and all). I met with John in 2015 and he made no false pretenses about the internal workings of this automaton. It may have been “brute force” but it proved a point: parts of a conversation can be made to appear “natural” using a sufficiently large definition of patterns. It proved Alan Turing’s assertion, that this question of a machine fooling humans was “meaningless”.

@@

One text classification algorithm is "Multinomial Naive Bayes." Given a training set of sentences, each belonging to a class (that is, a particular group), we can count the occurrence of each word in each class, account for its commonality and assign each word a score for each class. Factoring for commonality is important: matching the word “it” is considerably less meaningful than a match for the word “cheese”. When we input a new sentence, scores for each word in the new sentence are compared to scores for those same words in the training set. The class with the highest OVERALL score for the input sentence is the class to which the input sentence most likely belongs.

@@

I will be using an algorithm-based classification strategy for this project.

@@

###Neural Networks
A neural network is a mathematical model that is designed to behave similar to biological neurons and nervous system. These models are used to recognize complex patterns and relationships that exists within a labelled data.

Artificial neural networks, invented in the 1940’s, are a way of calculating an output from an input (a classification) using weighted connections (“synapses”) that are calculated from repeated iterations through training data. Each pass through the training data alters the weights such that the neural network produces the output with greater “accuracy” (lower error rate).

There’s not much new about these structures, except today’s software is using much faster processors and can work with a lot more memory. The combination of working memory and speed is crucial when you’re doing hundreds of thousands of matrix multiplications (the neural network’s essential math operation).

Each class is given with some number of example sentences. Once again each sentence is broken down by word (stemmed) and each word becomes an input for the neural network. The synaptic weights are then calculated by iterating through the training data thousands of times, each time adjusting the weights slightly to greater accuracy. By recalculating back across multiple layers (“back-propagation”) the weights of all synapses are calibrated while the results are compared to the training data output. These weights are like a ‘strength’ measure, in a neuron the synaptic weight is what causes something to be more memorable than not. You remember a thing more because you’ve seen it more times: each time the ‘weight’ increases slightly.

At some point the adjustment reaches a point of diminishing returns, this is called “over-fitting” and going beyond this is counter-productive.

The trained neural network is less code than an comparable algorithm but it requires a potentially large matrix of “weights”. In a relatively small sample, where the training sentences have 150 unique words and 30 classes this would be a matrix of 150x30. Imagine multiplying a matrix of this size 100,000 times to establish a sufficiently low error rate. This is where processing speed comes in.

If the neural network sounds magnificently sophisticated, relax, it boils down to matrix multiplication and a formula for reducing values between -1 and 1 or some other minimal range. A middle-school math student could learn this in a few hours. The hard work is achieving clean training data.

Just as there are variations in pattern matching code and in algorithms, there are variations in neural networks, some more complex than others. The basic machinery is the same. The essential work is that of classification.

Networks are looking for patterns in collections of terms, each term is reduced to a token. In this machine words have no meaning except for their patterned existence within training data. The label “artificial intelligence” applied to such machinery is mostly BS.

>>>>

---
title: "Choosing a Text Classifier Method"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

The many methods for classifying texts fall into three general categories:

*  Pattern matching strategies (does a particular phrase appear?)
*  Algorithms (how closely does the query text meet pre-set criteria?)
*  Neural networks (the network decides its own criteria; aka, machine learning)

This edited excerpt from a tutorial on chat-bots nicely describes the overall approach and problems of text classification, and the differences between pattern matching and algorithmic classifiers. For the original version go to: https://medium.com/@gk_/how-chat-bots-work-dfff656a35e2

@@

This classifier is "naive" because each word is treated as having no connection with other words in the sentence being classified. It assumes independence between "features," in this case, words.

For example, in the sentence "the fox jumped over the log", there is no relationship between "jumped" and "fox" or "log". In NLP, this collection of words is referred to as "a bag of words". While this is incredibly naive, the classifier isn’t attempting to understand the meaning of a sentence, it’s trying to classify it.

Pattern Matchers
Early chatbots used pattern matching to classify text and produce a response. This is often referred to as "brute force" as the author of the system needs to describe every pattern for which there is a response.

A standard structure for these patterns is "AIML" (artificial intelligence markup language). Its use of the term "artificial intelligence" is quite an embellishment, but that’s another story.

@@

It knows who a physicist is only because his or her name has an associated pattern. Likewise it responds to anything solely because of an authored pattern. Given hundreds or thousands of patterns you might see a chatbot "persona" emerge.

In 2000 a chatbot built by John Denning and colleagues using this approach was in the news for passing the "Turing test". It emulated the replies of a 13 year old boy from Ukraine (broken English and all). I met with John in 2015 and he made no false pretenses about the internal workings of this automaton. It may have been "brute force" but it proved a point: parts of a conversation can be made to appear "natural" using a sufficiently large definition of patterns. It proved Alan Turing’s assertion, that this question of a machine fooling humans was "meaningless".

@@

One text classification algorithm is "Multinomial Naive Bayes." Given a training set of sentences, each belonging to a class (that is, a particular group), we can count the occurrence of each word in each class, account for its commonality and assign each word a score for each class. Factoring for commonality is important: matching the word "it" is considerably less meaningful than a match for the word "cheese". When we input a new sentence, scores for each word in the new sentence are compared to scores for those same words in the training set. The class with the highest OVERALL score for the input sentence is the class to which the input sentence most likely belongs.

@@

@@

###Neural Networks
A neural network is a mathematical model that is designed to behave similarly to biological neurons and nervous systems. These models are used to recognize complex patterns and relationships that exists within a labeled dataset.

Artificial neural networks, invented in the 1940’s, calculate an output from an input (a classification) using weighted connections ("synapses") that are calculated from repeated iterations through training data. Each pass through the training data alters the weights such that the neural network produces the output with greater "accuracy" (lower error rate).

Each class is given with some number of example sentences. Each sentence is broken down by word (stemmed) and each word becomes an input for the neural network. The synaptic weights are then calculated by iterating through the training data thousands of times, each time adjusting the weights slightly to greater accuracy. By recalculating back across multiple layers ("back-propagation") the weights of all synapses are calibrated while the results are compared to the training data output. These weights are like a ‘strength’ measure, in a neuron the synaptic weight is what causes something to be more memorable than not. You remember a thing more because you’ve seen it more times: each time the ‘weight’ increases slightly.

At some point the adjustment reaches a point of diminishing returns, this is called "over-fitting" and going beyond this is counter-productive.

A fully trained neural network is less code than a comparable algorithm The neural network boils down to matrix multiplication and a formula for reducing values between -1 and 1 or some other minimal range. The challenge is that it requires a potentially large matrix of "weights". In a relatively small sample, where the training sentences have 150 unique words and 30 classes this would be a matrix of 150x30. Imagine multiplying a matrix of this size 100,000 times to establish a sufficiently low error rate.

This is where processing speed comes in. A combination of working memory and processor speed is crucial when you’re doing hundreds of thousands of matrix multiplications (the neural network’s essential math operation). Today’s software takes full advantage of faster processors and can work with a lot more memory.

The other hard part is obtaining clean training data, which is essential for proper classification.

Just as there are different pattern matching models and algorithms, there are different types of neural networks, some more complex than others. The basic machinery is the same. Networks are looking for patterns in collections of terms, each term is reduced to a token. In this machine words have no meaning except for their patterned existence within training data.

### 2019-03-13 aacr.Rmd
update

---
title: "Automated Analysis of Student Writing Writing "
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

There is growing need and interest in incorporating automated feedback into writing training. This raises important questions that have not yet been adequately answered:

*  Does automated feedback identify similar issues with similar frequency as live instructors?
*  When instructors have access to automated feedback, do they trust it? Do they provide feedback on different issues, focus on higher-order problems, or continue grading as if they had no insights?
*  Do students respond to automated feedback in the same way as feedback from live instructors?

@@

#How Did Automated Feedback Begin?
Interest in technology-assisted automated feedback on writing began in the mid-1960s. Systems have progressed from basic spelling and grammar checkers to automated essay scoring (AES) systems that provide feedback on the content of open-response writing. AES systems use natural language processing and machine learning algorithms to produce a score that is based on syntactic and lexical patterns and features such as sentence length, word frequency and part of speech [@Shermis2010, @Balfour2013].

AES systems have the advantage of being scalable and are very attractive for large face-to-face courses, and for asynchronous courses like massive open online courses [@Balfour2013]. Demand for AES systems has spurred development of several commercial products including Criterion®, WriteToLearn™, Intelligent Essay Assessor™, IntelliMetric®, WriteLab, Inc. and Turnitin Feedback Studio.

AES systems are not without drawbacks. First, it is controversial how accurately unsupervised AES systems score student work. Perelman [@Perelman2013] highlighted the poor accuracy of extant AES by using obviously faked texts to demonstrate how easily current AES applications are fooled. Second, it is unclear to what extent students pay attention to automated feedback. One small study [@Heffernan2015] compared relative impacts of teacher feedback versus technology driven feedback from ETS' Criterion® tool on 12 Japanese English-foreign- language students' writing. Results showed automated feedback alone was less effective than feedback from the teacher and Criterion® combined. However, the authors only compared scores on three independent, consecutive writing assignments; they did not compare effects of feedback on draft versus final versions of the same assignment. Also, the authors failed to compare automated feedback alone to teachers' comments alone. The degree of authority that students attach to automated feedback may also be a confounding variable. Ruegg [@Ruegg2015] found that feedback from peer reviewers was not valued as much as teachers' feedback, even though teachers provided less explicit comments than peer reviewers. Ruegg argued that this is likely because teachers are the ones that ultimately grade the student's writing. More research is needed to improve AES systems and to test their effectiveness in the classroom.

Despite their limitations, demand remains high for AES systems, and there are ongoing efforts to integrate them into more traditional writing review models [@Balfour2013]. Constructed response assessments reveal more about student thinking and the persistence of misconceptions than do multiple-choice questions. However they require more analysis on the part of the educator, and so are less likely to be used in large-enrollment courses. Urban-Lurain and colleagues developed automated assessment of constructed response (AACR) as a way to give students constructed response test questions and other work that can be graded automatically [@Kaplan2014, @Weston2015, @Ha2015, @Urban-Lurain2015, @Ha2016]. AACR uses a robust and scalable platform for scoring open responses to pre-written prompts that probe important disciplinary concepts from biology and biological chemistry. The prompts are administered via online course management systems where students enter responses. Lexical and statistical analyses then predict what expert ratings would be for student responses. Work to date shows that automated analyses can predict expert ratings of students' work on these topics accurately and with higher inter-rater reliability than a group of trained human graders. The AACR model is growing rapidly to include additonal STEM disicplines and has a national presence (http://create4stem.msu.edu/project/aacr). 
The success of AACR would suggest that the general lexical analysis principles this project is based on can be applied to the analysis of student writing. Our NSF-sponsored propoosal is exploring whether automated feedback affect how graduate teaching assistants (TAs) grade writing-related activities. Using the text classifier being built for this FLC project, we will determine whether TAs provide students with more feedback focused on higher order thinking, and less on low-level copy editing.

>>>>

---
title: "Automated Feedback on Student Writing"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

There is growing need and interest in using automated feedback as part of writing training. This raises important questions that have not yet been adequately answered:

*  Can/do automated feedback systems identify similar issues as live instructors, with similar frequency?
*  When instructors have access to automated feedback, do they trust it? Do they provide feedback on different issues, focus on higher-order problems, or continue grading as if they had no insights?
*  Do students respond to automated feedback in the same way as feedback from live instructors?

@@

#Origins of Automated Feedback
Interest in automated feedback on writing emerged in the mid-1960s. Systems have since progressed from basic spelling checkers to syntax-aware spelling and grammar evaluation. More recently, automated essay scoring (AES) systems emerged that can provide feedback on open-response writing. AES systems use natural language processing and machine learning algorithms to produce a score based on syntactic and lexical patterns and features such as sentence length, word frequency and part of speech [@Shermis2010, @Balfour2013].

Demand for AES systems has spurred development of several commercial products including Criterion®, WriteToLearn™, Intelligent Essay Assessor™, IntelliMetric®, WriteLab, Inc. and Turnitin Feedback Studio.

AES systems have the advantage of being scalable and are very attractive for large face-to-face courses, and for asynchronous courses like massive open online courses [@Balfour2013]. Still they are not without drawbacks. First, un-/minimally-supervised AES systems may not score student work consistently. Perelman [@Perelman2013] highlighted their poor accuracy, using obviously faked texts to demonstrate how easily current AES applications are fooled. Second, it is unclear to what extent students pay attention to automated feedback. One small study [@Heffernan2015] compared relative impacts of teacher feedback versus technology driven feedback from ETS' Criterion® tool on 12 Japanese English-foreign- language students' writing. Results showed automated feedback alone was less effective than feedback from the teacher and Criterion® combined. However, the authors only compared scores on three independent, consecutive writing assignments; they did not compare effects of feedback on draft versus final versions of the same assignment. Also, the authors failed to compare automated feedback alone to teachers' comments alone.

The degree of authority students attach to both automated and human feedback also is a confounding variable. Anecdotally, most instructors can cite many examples of students ignoring basic spelling and grammar feedback that is standard for word processors like MS. Word. Ruegg [@Ruegg2015] found that feedback from peer reviewers was not valued as much as teachers' feedback, even though teachers provided less explicit comments than peer reviewers. Ruegg argued that this is likely because teachers are the ones that ultimately grade the student's writing.

Despite their limitations, demand remains high for AES systems, and there are ongoing efforts to integrate them into more traditional writing review models [@Balfour2013]. Constructed response assessments reveal more about student thinking and the persistence of misconceptions than do multiple-choice questions. However they require more analysis on the part of the educator, and so are less likely to be used in large-enrollment courses. Urban-Lurain and colleagues developed automated assessment of constructed response (AACR) as a way to give students constructed response test questions and other work that can be graded automatically [@Kaplan2014, @Weston2015, @Ha2015, @Urban-Lurain2015, @Ha2016]. AACR uses a robust and scalable platform for scoring open responses to pre-written prompts that probe important disciplinary concepts from biology and biological chemistry. The prompts are administered via online course management systems where students enter responses. Lexical and statistical analyses then predict what expert ratings would be for student responses. Work to date shows that automated analyses can predict expert ratings of students' work on these topics accurately and with higher inter-rater reliability than a group of trained human graders. The AACR model is growing rapidly to include additonal STEM disicplines and has a national presence (http://create4stem.msu.edu/project/aacr).

The success of AACR **suggests** that the general lexical analysis principles this project is based on can be applied to the analysis of student writing. However, more research is needed before we can say with any confidence that automated feedback benefits students or their instructors.

Our NSF-sponsored propoosal is exploring whether automated feedback affect how graduate teaching assistants (TAs) grade writing-related activities. Using the text classifier being built for this FLC project, we will determine whether TAs provide students with more feedback focused on higher order thinking, and less on low-level copy editing.

### 2019-03-13 build.Rmd
update

**Extracting TAs' Comments** *(Early coding stage)*  
Protocol used to extract TA comments from student lab reports.  
https://adanieljohnson.github.io/default_website/docxcommentextraction.html

**Structure of Development Dataset; Data Import & Validation** *(Completed)*  
Organization of the initial dataset, and how data were imported in R and validated.  
https://adanieljohnson.github.io/default_website/dataimport.html

**Codebook for Classifying TAs' Comments** *(Completed)*  
Describes the process for developing the codes used to classify comments.  
https://adanieljohnson.github.io/default_website/codebook.html

**Initial Exploration of the Dataset** *(Partly completed)*  
What is the distribution of words used in the TA comments?  
https://adanieljohnson.github.io/default_website/initial_exploration.html

**Current Version of the Naive Bayes Comment Classifier** *(Completed)*  
Code for the most recent version of the optimized NB classifier.   
https://adanieljohnson.github.io/default_website/NB_2r2c.html

**Embedding the Naive Bayes Classifier in an Ensemble Model** *(Planning stage)*  
The NB method alone does not classify TA comments with sufficient accuracy for the "Structure" category. This page outlines a vertically stacked "ensemble" classifier that uses pattern matching and other pre-processing steps to improve NB accuracy.
https://adanieljohnson.github.io/default_website/Ensemble_Notes.html

>>>>

####\

####Extracting TAs' Comments 
*(Early coding stage)*  
Protocol used to extract TA comments from student lab reports.  
https://adanieljohnson.github.io/default_website/docxcommentextraction.html

####Structure of Development Dataset; Data Import & Validation 
*(Completed)*  
Organization of the initial dataset, and how data were imported in R and validated.  
https://adanieljohnson.github.io/default_website/dataimport.html

####Codebook for Classifying TAs' Comments 
*(Completed)*  
Describes the process for developing the codes used to classify comments.  
https://adanieljohnson.github.io/default_website/codebook.html

####Initial Exploration of the Dataset 
*(Partly completed)*  
What is the distribution of words used in the TA comments?  
https://adanieljohnson.github.io/default_website/initial_exploration.html

####Current Version of the Naive Bayes Comment Classifier 
*(Completed)*  
Code for the most recent version of the optimized NB classifier.   
https://adanieljohnson.github.io/default_website/NB_2r2c.html

####Embedding the Naive Bayes Classifier in an Ensemble Model  
*(Planning stage)*
The NB method alone does not classify TA comments with sufficient accuracy for the "Structure" category. This page outlines a vertically stacked "ensemble" classifier that uses pattern matching and other pre-processing steps to improve NB accuracy.
https://adanieljohnson.github.io/default_website/Ensemble_Notes.html

### 2019-03-13 litreview.Rmd
update

---
title: "Literature Review"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

**Challenges of Teaching Technical Writing**  
More than 50% of colleges and universities use some form of Writing in the Disciplines, Write to Learn, and Writing Across the Curriculum (WID/WTL/WAC) as part of their general education programs. There are well-established WAC/WID teaching principles based on >40 years of evidence and experience, but much of this work focuses on non-technical styles of writing. We know much less about teaching technical writing specifically. What do we know, and what can we bring from the WAC/WID community? What do we NOT know?  
https://adanieljohnson.github.io/default_website/techwriting.html

**Challenges of Training Future Faculty**  
A major barrier to routine writing in STEM is limited instructor awareness of evidence-based training models. Many college STEM teachers have never been introduced to proven writing training strategies or trained to give effective, context-specific feedback. How does this impact instruction more generally?  
https://adanieljohnson.github.io/default_website/futurefaculty.html

**Challenges of Applying Automated Text Analysis to Student Learning**  
Interest in technology-assisted automated feedback on writing began in the mid-1960s. Systems have progressed from basic spelling and grammar checkers to automated essay scoring (AES) systems that provide feedback on the content of open-response writing. Can automated text analysis support student learning?  
https://adanieljohnson.github.io/default_website/aacr.html

**Text Classification 1 - Feature Selection and Engineering**  
What is the general strategy and steps for solving a text classification problem? What features are important? 
https://adanieljohnson.github.io/default_website/Text_Classifier_Models.html

**Text Classification 2 - Topic Categorization and Modeling**  
Establishing meaningful text classification categories depends on the goals of the project or the question being asked. Are relevant categories known already? If not, how are they established?  
https://adanieljohnson.github.io/default_website/Topic_categorization.html

**Text Classification 3 - Selecting an Appropriate Classifier Method**  
There are three general classes of text classification strategies: pattern matching, algorithmic, and neural networks. Each is described briefly.  
https://adanieljohnson.github.io/default_website/Choosing_classifier.html

**Text Classification 4 - Evaluating and Improving the Classifier**  
If there are many ways to classify texts, how do we know which one is most accurate? How can we improve the classification process? How do we make comparisons and evaluate the different steps in a text classification problem?  
https://adanieljohnson.github.io/default_website/Improving_classifier.html

>>>>

---
title: "Literature Review"
date: "Updated `r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

####\

####Challenges of Teaching Technical Writing
More than 50% of colleges and universities use some form of Writing in the Disciplines, Write to Learn, and Writing Across the Curriculum (WID/WTL/WAC) as part of their general education programs. There are well-established WAC/WID teaching principles based on >40 years of evidence and experience, but much of this work focuses on non-technical styles of writing. We know much less about teaching technical writing specifically. What do we know, and what can we bring from the WAC/WID community? What do we NOT know?  
https://adanieljohnson.github.io/default_website/techwriting.html

####Challenges of Training Future Faculty
A major barrier to routine writing in STEM is limited instructor awareness of evidence-based training models. Many college STEM teachers have never been introduced to proven writing training strategies or trained to give effective, context-specific feedback. How does this impact instruction more generally?  
https://adanieljohnson.github.io/default_website/futurefaculty.html

####Challenges of Applying Automated Text Analysis to Student Learning
Interest in technology-assisted automated feedback on writing began in the mid-1960s. Systems have progressed from basic spelling and grammar checkers to automated essay scoring (AES) systems that provide feedback on the content of open-response writing. Can automated text analysis support student learning?  
https://adanieljohnson.github.io/default_website/aacr.html

####Text Classification 1 - Feature Selection and Engineering
What is the general strategy and steps for solving a text classification problem? What features are important? 
https://adanieljohnson.github.io/default_website/Text_Classifier_Models.html

####Text Classification 2 - Topic Categorization and Modeling
Establishing meaningful text classification categories depends on the goals of the project or the question being asked. Are relevant categories known already? If not, how are they established?  
https://adanieljohnson.github.io/default_website/Topic_categorization.html

####Text Classification 3 - Selecting an Appropriate Classifier Method
There are three general classes of text classification strategies: pattern matching, algorithmic, and neural networks. Each is described briefly.  
https://adanieljohnson.github.io/default_website/Choosing_classifier.html

####Text Classification 4 - Evaluating and Improving the Classifier
If there are many ways to classify texts, how do we know which one is most accurate? How can we improve the classification process? How do we make comparisons and evaluate the different steps in a text classification problem?  
https://adanieljohnson.github.io/default_website/Improving_classifier.html

### 2019-03-13 techwriting.Rmd
update

```{r, child="_setup.Rmd"}
```
Strong scientific thinking & communication skills are essential for 21st century STEM workers [@Anderman2011, @CWPA2011, @PCAST2012], but there are not enough college graduates with these skills to meet projected US workforce demands [@AACU2007, @BHEF2011, @Carnevale2011]. Policy makers have called on educators to prioritize development of career-relevant “21st-century skills” [@CWPA2011, @NRC2010, @NRC2012, @Starke-Meyerring2011]. These include quantitative and information literacy, adaptability, novel problem-solving, self-regulation, systems thinking, analytical and critical thinking skills, and complex communication skills [@Anderman2011] A more scientifically and computationally literate citizenry also will be better prepared to evaluate personal choices, societal issues, and larger policies that have deep connections to science and technology [@PCAST2012].

@@

#Future Faculty Need Training on How to Teach Scientific Writing
This project focuses specifically on improving the feedback process in two ways. First, the training program teaches instructors how to give holistic feedback that is individualized and context-specific. Second, students will receive a portion of their feedback from SAWHET, a technology-assisted, automated feedback system.

>>>>

```{r, child="_setup.Rmd"}
```
Strong scientific thinking & communication skills are essential for 21st century STEM workers [@Anderman2011, @CWPA2011, @PCAST2012], but there are not enough college graduates with these skills to meet projected US workforce demands [@AACU2007, @BHEF2011, @Carnevale2011]. Policy makers have called on educators to prioritize development of "career-relevant 21st-century skills” [@CWPA2011, @NRC2010, @NRC2012, @Starke-Meyerring2011]. These include quantitative and information literacy, adaptability, novel problem-solving, self-regulation, systems thinking, analytical and critical thinking skills, and complex communication skills [@Anderman2011] A more scientifically and computationally literate citizenry also will be better prepared to evaluate personal choices, societal issues, and larger policies that have deep connections to science and technology [@PCAST2012].

@@

#Faculty Need Training to Teach Technical Writing Well
This project focuses specifically on improving the feedback process in two ways. First, the training program teaches instructors how to give holistic feedback that is individualized and context-specific. Second, students will receive a portion of their feedback from SAWHET, a technology-assisted, automated feedback system.
